\documentclass[a4paper,oneside,11.000000pt]{book}

\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{a4wide}
\usepackage{url}
\usepackage{float}
\usepackage{layouts}
\usepackage{supertabular}
\usepackage{titlesec}
\usepackage{listings}
\usepackage{syntax}
\usepackage[colorlinks=true,linkcolor=blue]{hyperref}
\setcounter{secnumdepth}{10}
\setcounter{tocdepth}{4}

\titleformat{\chapter}[hang]{\bf\Huge}{\arabic{chapter}}{1em}{}{}
\titleclass{\subchapter}{straight}[\chapter]
\newcounter{subchapter}
\renewcommand{\thesubchapter}{\thechapter.\arabic{subchapter}}
\titleformat{\subchapter}[hang]{\bf\huge}{\thesubchapter}{0.5em}{}{}
\titlespacing{\subchapter}{0pt}{0pt}{0pt}
\renewcommand\thesection{\thesubchapter.\arabic{section}}
\makeatletter
\newcommand*\l@subchapter{\@dottedtocline{1}{1.5em}{2.3em}}
\renewcommand\l@section{\@dottedtocline{2}{3.8em}{3.2em}}
\renewcommand\l@subsection{\@dottedtocline{3}{7em}{4.1em}}
\renewcommand\l@subsubsection{\@dottedtocline{4}{11.1em}{5em}}
\makeatother

\makeatletter
\renewcommand\subparagraph{\@startsection{subparagraph}{5}{0mm}{-\baselineskip}{0.5\baselineskip}{\normalfont\normalsize\scshape}}
\makeatother

\lstdefinelanguage{Cmajor}{morekeywords={bool, true, false, sbyte, byte, short, ushort, int, uint, long, ulong, float, double, char, void, enum, cast, namespace, using, static, extern, is, explicit, delegate, inline, cdecl, nothrow, public, protected, private, internal, virtual, abstract, override, suppress, default, operator, class, return, if, else, switch, case, default, while, do, for, break, continue, goto, typedef, typename, const, null, this, base, construct, destroy, new, delete, sizeof, try, catch, throw, concept, where, axiom, and, or, not},sensitive=true,morecomment=[l]{//},morecomment=[s]{/*}{*/},morestring=[b]",morestring=[b]',}\lstloadlanguages{Cmajor}
\lstset{language=Cmajor,showstringspaces=false,breaklines=true,basicstyle=\small}
\makeatletter\def\toclevel@chapter{0}\def\toclevel@subchapter{1}\def\toclevel@section{2}\def\toclevel@subsection{3}\def\toclevel@subsubsection{4}\makeatother\begin{document}
\clearpage

\frontmatter
\title{\textsc{System.Numerics.Multiprecision Library Reference}
}
\date{\today}
\maketitle
\tableofcontents

\clearpage
\chapter{Description}
\begin{flushleft}
\hyperlink{System.Numerics.Multiprecision}{Multiprecision} is a multiple precision arithmetic library.
The library is implemented using GNU Multiple Precision Arithmetic Library 
(\url{http://gmplib.org/}).

\end{flushleft}
\chapter{Namespaces}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{7.44777cm}!{\raggedright}p{7.70223cm}}
\textbf{Namespace}
& \textbf{Description}
\\
\hline
\hyperlink{System.Numerics.Multiprecision}{System.Numerics.Multiprecision}
& Contains arbitrary precision signed integer type \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\\
\end{supertabular}

\end{flushleft}
\clearpage
\mainmatter

\chapter{Usage}

\section{Referencing the System.Numerics.Multiprecision library}

Right-click a project node in IDE \verb.|. Project References... \verb.|.
Add System Extension Library Reference... \verb.|.
enable \emph{System.Numerics.Multiprecision} check box

\begin{flushleft}
or add following line to your project's .cmp file:
\begin{verbatim}
reference <ext/System.Numerics.Multiprecision/System.Numerics.Multiprecision.cml>;
\end{verbatim}
\end{flushleft}

\chapter{Installation}

The System.Numerics.Multiprecision library uses the GNU MP library
that is precompiled for the following platforms:

\begin{itemize}
\item 32-bit Windows (x86)
\item 64-bit Windows (x64)
\item 32-bit PC Linux (i686)
\item 64-bit PC Linux (x86\_64)
\end{itemize}

Current version of GNU MP library at the time of writing is 6.1.0.

If you want to install newer version of the GNU MP library or
if you have different platform, you can compile the GNU MP library from sources
by using the following instructions.

\section{Compiling the GNU MP library from sources in Windows}

\begin{itemize}

\item
Install MinGW-w64 GCC to a path that does not contain spaces.
I have mine installed in \verb|C:\mingw-w64|.

Installer can be obtained from\\
\url{http://sourceforge.net/projects/mingw-w64/files/Toolchains%20targetting%20Win32/Personal%20Builds/mingw-builds/installer/mingw-w64-install.exe/download}

\item
Install MSYS2.
Installation instructions can be found in\\
\url{http://sourceforge.net/p/msys2/wiki/MSYS2%20installation/}

I have mine installed in \verb|C:\msys64|.

\item
Start MSYS2 shell.

\item
In the MSYS2 shell obtain \textbf{tar} by executing
\begin{verbatim}
pacman -S tar
\end{verbatim}

\item
Obtain \textbf{make} by executing
\begin{verbatim}
pacman -S make
\end{verbatim}

\item
Mount your MinGW-directory (mine is in \verb|C:/mingw-w64|) by executing
\begin{verbatim}
mkdir /mingw
mount C:/mingw-w64 /mingw
\end{verbatim}

\item
Insert your MinGW bin-directory in front of the PATH by executing
\begin{verbatim}
export PATH=/mingw/mingw64/bin:$PATH
\end{verbatim}

\item
Now if you ask which GCC is used by executing
\begin{verbatim}
which gcc
\end{verbatim}
you should get \textbf{/mingw/mingw64/bin/gcc}.

\item
Download the GNU MP library from \url{http://gmplib.org/#DOWNLOAD} in bz2 format
and place it to your MSYS2 home directory (mine is in \verb|C:\msys64\home\Seppo|).

\item
Extract the GNU MP library by executing
\begin{verbatim}
tar xjf gmp-6.1.0.tar.bz2
\end{verbatim}

\item
Change to gmp-directory by executing
\begin{verbatim}
cd gmp-6.1.0
\end{verbatim}

\item
Configure the library for 64-bit Windows by executing
\begin{verbatim}
./configure --enable-static --disable-shared --host=x86_64-w64-mingw32
\end{verbatim}

For 32-bit Windows the command is
\begin{verbatim}
./configure --enable-static --disable-shared --host=i686-w64-mingw32
\end{verbatim}

Shared libraries are not used in Cmajor so we are disabling them.

\item
Make the library by executing
\begin{verbatim}
make
\end{verbatim}

\item
Install the library by executing
\begin{verbatim}
make install
\end{verbatim}

\item
Optionally test the library by executing
\begin{verbatim}
make check
\end{verbatim}

\item
Now the header file \textbf{gmp.h} should be in \verb|C:\msys64\usr\local\include| directory
and the library file \textbf{libgmp.a} should be in \verb|C:\msys64\usr\local\lib| directory.
Copy gmp.h and libgmp.a under the Cmajor System.Numerics.GmpIntf extension library to directory

\begin{verbatim}
%APPDATA%\Cmajor\system\ext\System.Numerics.GmpIntf\gmp\windows\x64
\end{verbatim}
for 64-bit Windows, or to
\begin{verbatim}
%APPDATA%\Cmajor\system\ext\System.Numerics.GmpIntf\gmp\windows\x86
\end{verbatim}
for 32-bit Windows.

\item
That's all.

\end{itemize}

\section{Compiling the GNU MP library from sources in Linux}

\begin{itemize}

\item
Download the GNU MP library from \url{http://gmplib.org/#DOWNLOAD} in bz2 format
and place it to your home directory.

\item
Extract the GNU MP library by executing
\begin{verbatim}
tar xjf gmp-6.1.0.tar.bz2
\end{verbatim}

\item
Change to gmp-directory by executing
\begin{verbatim}
cd gmp-6.1.0
\end{verbatim}

\item
Configure the library by executing
\begin{verbatim}
./configure --enable-static --disable-shared
\end{verbatim}

Shared libraries are not used in Cmajor so we are disabling them.

\item
Make the library by executing
\begin{verbatim}
make
\end{verbatim}

\item
Install the library by executing
\begin{verbatim}
make install
\end{verbatim}

\item
Optionally test the library by executing
\begin{verbatim}
make check
\end{verbatim}

\item
Now the header file \textbf{gmp.h} should be in \verb|/usr/local/include| directory
and the library file \textbf{libgmp.a} should be in \verb|/usr/local/lib| directory.
Copy gmp.h and libgmp.a under the Cmajor System.Numerics.GmpIntf extension library to 
\begin{verbatim}
<your cmajor directory>/system/ext/System.Numerics.GmpIntf/gmp/linux/x86_64
\end{verbatim}
directory for 64-bit Linux or to 
\begin{verbatim}
<your cmajor directory>/system/ext/System.Numerics.GmpIntf/gmp/linux/i686
\end{verbatim}
directory for 32-bit Linux.

\item
That's all.

\end{itemize}


\hypertarget{System.Numerics.Multiprecision}{\chapter{System.Numerics.Multiprecision Namespace}}
\begin{flushleft}
Contains arbitrary precision signed integer type \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\end{flushleft}
\clearpage
\subchapter{Classes}
\begin{flushleft}
\begin{supertabular}[l]{ll}
\textbf{Class}
& \textbf{Description}
\\
\hline
\hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}
& An arbitrary precision signed integer type.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt}{\section{BigInt Class}}\begin{flushleft}
An arbitrary precision signed integer type.

\end{flushleft}

\subsection*{Syntax}\texttt{public class BigInt;}
\subsection{Member Functions}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{7.575cm}!{\raggedright}p{7.575cm}}
\textbf{Member Function}
& \textbf{Description}
\\
\hline
\hyperlink{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt}{BigInt()}
& Default constructor. Creates an instance of arbitrary precision signed integer and initializes it to zero.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{BigInt(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Copy constructor.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.operator.assign.P.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{operator=(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Copy assignment.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.RR.System.Numerics.Multiprecision.BigInt}{BigInt(System.\-Numerics.\-Multiprecision.\-BigInt\&\-\&\-)}
& Move constructor.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.operator.assign.P.System.Numerics.Multiprecision.BigInt.RR.System.Numerics.Multiprecision.BigInt}{operator=(System.\-Numerics.\-Multiprecision.\-BigInt\&\-\&\-)}
& Move assignment.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.C.R.System.String}{BigInt(const System.\-String\&\-)}
& Creates an instance of arbitrary precision signed integer and initializes it from provided decimal digit string.
Digit string may be prefixed by a sign character.
Throws \textbf{System.ConversionException} if a character other than sign or 0-9 is encountered in digit string.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.C.R.System.String.int}{BigInt(const System.\-String\&\-, int)}
& Creates an instance of arbitrary precision signed integer and initializes it from provided digit string.
Digit string may be prefixed by a sign character.
Digits must be in given base.
Throws \textbf{System.ConversionException} if a character other than sign or valid digit character is encountered.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.int}{BigInt(int)}
& Creates an instance of arbitrary precision signed integer and initializes it to given signed integer value.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.uint}{BigInt(uint)}
& Creates an instance of arbitrary precision signed integer and initializes it to given unsigned integer value.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.Handle.C.P.System.Numerics.Multiprecision.BigInt}{Handle() const}
& Returns a handle to the GNU MP library arbitrary precision integer representation.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.ToString.C.P.System.Numerics.Multiprecision.BigInt}{ToString() const}
& Returns the value of the \textbf{BigInt}
 as a string of decimal digits prefixed by minus sign if the value is negative.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.ToString.C.P.System.Numerics.Multiprecision.BigInt.int}{ToString(int) const}
& Returns the value of the \textbf{BigInt}
 as a string of digits in given base prefixed by minus sign if the value is negative.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.operator.assign.P.System.Numerics.Multiprecision.BigInt.int}{operator=(int)}
& Assigns the value of the \textbf{BigInt}
 to given signed integer value.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.operator.assign.P.System.Numerics.Multiprecision.BigInt.uint}{operator=(uint)}
& Assigns the value of the \textbf{BigInt}
 to given unsigned integer value.

\\
\hyperlink{System.Numerics.Multiprecision.BigInt.destructor.P.System.Numerics.Multiprecision.BigInt}{$\sim$BigInt()}
& Frees memory occupied by the \textbf{BigInt}
 instance.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt}{\subsubsection*{BigInt() Member Function}}
\begin{flushleft}
Default constructor. Creates an instance of arbitrary precision signed integer and initializes it to zero.

\end{flushleft}
\subsubsection*{Syntax}\texttt{public BigInt();}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{BigInt(const System.Numerics.Multiprecision.BigInt\&) Member Function}}\begin{flushleft}
Copy constructor.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public BigInt(const System.Numerics.Multiprecision.BigInt\& that);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{4.93333cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
that
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& A \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} to copy from.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.operator.assign.P.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator=(const System.Numerics.Multiprecision.BigInt\&) Member Function}}\begin{flushleft}
Copy assignment.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public void operator=(const System.Numerics.Multiprecision.BigInt\& that);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{4.6205cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
that
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& A \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} to assign.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.RR.System.Numerics.Multiprecision.BigInt}{\subsubsection*{BigInt(System.Numerics.Multiprecision.BigInt\&\&) Member Function}}\begin{flushleft}
Move constructor.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public BigInt(System.Numerics.Multiprecision.BigInt\&\& that);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{4.93333cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
that
& \hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt\&\-\&\-}
& A \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} to move from.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.operator.assign.P.System.Numerics.Multiprecision.BigInt.RR.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator=(System.Numerics.Multiprecision.BigInt\&\&) Member Function}}\begin{flushleft}
Move assignment.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public void operator=(System.Numerics.Multiprecision.BigInt\&\& that);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{4.6205cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
that
& \hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt\&\-\&\-}
& A \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} to assign.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.C.R.System.String}{\subsubsection*{BigInt(const System.String\&) Member Function}}
\begin{flushleft}
Creates an instance of arbitrary precision signed integer and initializes it from provided decimal digit string.
Digit string may be prefixed by a sign character.
Throws \textbf{System.ConversionException} if a character other than sign or 0-9 is encountered in digit string.

\end{flushleft}
\subsubsection*{Syntax}\texttt{public BigInt(const System.String\& str);}

\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{lll}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
str
& const System.\-String\&\-
& A string of decimal digits.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.C.R.System.String.int}{\subsubsection*{BigInt(const System.String\&, int) Member Function}}
\begin{flushleft}
Creates an instance of arbitrary precision signed integer and initializes it from provided digit string.
Digit string may be prefixed by a sign character.
Digits must be in given base.
Throws \textbf{System.ConversionException} if a character other than sign or valid digit character is encountered.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public BigInt(const System.String\& str, int base\_);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{4.63128cm}!{\raggedright}p{5.23538cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
str
& const System.\-String\&\-
& A string of digits of base \hyperlink{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.C.R.System.String.int.base\_}{base\_\-}.

\\
base\_
& int
& Base of digits. Base may vary from 2 to 62.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Remarks}
\begin{flushleft}
For bases up to 36, case is ignored; upper-case and lower-case letters have the same value. 
For bases 37 to 62, upper-case letter represent the usual 10..35 while lower-case letter represent 36..61.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.int}{\subsubsection*{BigInt(int) Member Function}}
\begin{flushleft}
Creates an instance of arbitrary precision signed integer and initializes it to given signed integer value.

\end{flushleft}
\subsubsection*{Syntax}\texttt{public BigInt(int that);}

\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{lll}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
that
& int
& A signed integer value.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.constructor.P.System.Numerics.Multiprecision.BigInt.uint}{\subsubsection*{BigInt(uint) Member Function}}
\begin{flushleft}
Creates an instance of arbitrary precision signed integer and initializes it to given unsigned integer value.

\end{flushleft}
\subsubsection*{Syntax}\texttt{public BigInt(uint that);}

\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{lll}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
that
& uint
& An unsigned integer value.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.Handle.C.P.System.Numerics.Multiprecision.BigInt}{\subsubsection*{Handle() const Member Function}}
\begin{flushleft}
Returns a handle to the GNU MP library arbitrary precision integer representation.

\end{flushleft}
\subsubsection*{Syntax}\texttt{public void* Handle() const;}

\subsubsection*{Returns}void*
\begin{flushleft}
Returns a handle to the GNU MP library arbitrary precision integer representation.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.ToString.C.P.System.Numerics.Multiprecision.BigInt}{\subsubsection*{ToString() const Member Function}}
\begin{flushleft}
Returns the value of the \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} as a string of decimal digits prefixed by minus sign if the value is negative.

\end{flushleft}
\subsubsection*{Syntax}\texttt{public System.String ToString() const;}

\subsubsection*{Returns}System.\-String
\begin{flushleft}
Returns the value of the \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} as a string of decimal digits prefixed by minus sign if the value is negative.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.ToString.C.P.System.Numerics.Multiprecision.BigInt.int}{\subsubsection*{ToString(int) const Member Function}}
\begin{flushleft}
Returns the value of the \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} as a string of digits in given base prefixed by minus sign if the value is negative.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.String ToString(int base\_) const;}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{lll}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
base\_
& int
& Base of digits. Base may vary from 2 to 62.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}System.\-String
\begin{flushleft}
Returns the value of the \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} as a string of digits in given base prefixed by minus sign if the value is negative.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.operator.assign.P.System.Numerics.Multiprecision.BigInt.int}{\subsubsection*{operator=(int) Member Function}}
\begin{flushleft}
Assigns the value of the \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} to given signed integer value.

\end{flushleft}
\subsubsection*{Syntax}\texttt{public void operator=(int that);}

\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{lll}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
that
& int
& A signed integer value.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.operator.assign.P.System.Numerics.Multiprecision.BigInt.uint}{\subsubsection*{operator=(uint) Member Function}}
\begin{flushleft}
Assigns the value of the \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} to given unsigned integer value.

\end{flushleft}
\subsubsection*{Syntax}\texttt{public void operator=(uint that);}

\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{lll}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
that
& uint
& An unsigned integer value.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.BigInt.destructor.P.System.Numerics.Multiprecision.BigInt}{\subsubsection*{$\sim$BigInt() Member Function}}
\begin{flushleft}
Frees memory occupied by the \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} instance.

\end{flushleft}
\subsubsection*{Syntax}\texttt{public $\sim$BigInt();}

\subsection{Nonmember Functions}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{7.575cm}!{\raggedright}p{7.575cm}}
\textbf{Function}
& \textbf{Description}
\\
\hline
\hyperlink{System.Numerics.Multiprecision.Abs.C.R.System.Numerics.Multiprecision.BigInt}{Abs(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns absolute value of given \textbf{BigInt}
.

\\
\hyperlink{System.Numerics.Multiprecision.ClearBit.R.System.Numerics.Multiprecision.BigInt.uint}{ClearBit(System.\-Numerics.\-Multiprecision.\-BigInt\&\-, uint)}
& Clear given bit of given \textbf{BigInt}
.

\\
\hyperlink{System.Numerics.Multiprecision.SetBit.R.System.Numerics.Multiprecision.BigInt.uint}{SetBit(System.\-Numerics.\-Multiprecision.\-BigInt\&\-, uint)}
& Set given bit of given \textbf{BigInt}
.

\\
\hyperlink{System.Numerics.Multiprecision.TestBit.R.System.Numerics.Multiprecision.BigInt.uint}{TestBit(System.\-Numerics.\-Multiprecision.\-BigInt\&\-, uint)}
& Returns true if given bit of given \textbf{BigInt}
 is set, false otherwise.

\\
\hyperlink{System.Numerics.Multiprecision.ToggleBit.R.System.Numerics.Multiprecision.BigInt.uint}{ToggleBit(System.\-Numerics.\-Multiprecision.\-BigInt\&\-, uint)}
& Toggle given bit of given \textbf{BigInt}
.

\\
\hyperlink{System.Numerics.Multiprecision.operator.remainder.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{operator\%(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-, const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns the remainder when given \textbf{BigInt}
 is divided by another.

\\
\hyperlink{System.Numerics.Multiprecision.operator.and.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{operator\&\-(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-, const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns bitwise AND of two \textbf{BigInt}
 values.

\\
\hyperlink{System.Numerics.Multiprecision.operator.times.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{operator*(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-, const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns the product of given \textbf{BigInt}
 value multiplied by another.

\\
\hyperlink{System.Numerics.Multiprecision.operator.plus.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{operator+(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-, const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns the sum of given \textbf{BigInt}
 value added to another.

\\
\hyperlink{System.Numerics.Multiprecision.operator.minus.C.R.System.Numerics.Multiprecision.BigInt}{operator-(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns the negation of \textbf{BigInt}
.

\\
\hyperlink{System.Numerics.Multiprecision.operator.minus.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{operator-(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-, const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns the difference of given \textbf{BigInt}
 value subtracted from another.

\\
\hyperlink{System.Numerics.Multiprecision.operator.divides.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{operator/(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-, const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns the quotient when given \textbf{BigInt}
 is divided by another.

\\
\hyperlink{System.Numerics.Multiprecision.operator.less.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{operator$<$\-(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-, const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns true if the first \textbf{BigInt}
 is less than the second \textbf{BigInt}
, false otherwise.

\\
\hyperlink{System.Numerics.Multiprecision.operator.shiftLeft.R.System.IO.OutputStream.C.R.System.Numerics.Multiprecision.BigInt}{operator$<$\-$<$\-(System.\-IO.\-OutputStream\&\-, const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Puts the value of the given \textbf{BigInt}
 to the given output stream as string of decimal digits prefixed by minus sign if the value is negative.

\\
\hyperlink{System.Numerics.Multiprecision.operator.equal.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{operator==(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-, const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns true if the first \textbf{BigInt}
 is equal to the second \textbf{BigInt}
, false otherwise.

\\
\hyperlink{System.Numerics.Multiprecision.operator.xor.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{operator\^{}(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-, const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns bitwise XOR of two \textbf{BigInt}
 values.

\\
\hyperlink{System.Numerics.Multiprecision.operator.or.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{operator|(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-, const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns bitwise inclusive OR of two \textbf{BigInt}
 values.

\\
\hyperlink{System.Numerics.Multiprecision.operator.complement.C.R.System.Numerics.Multiprecision.BigInt}{operator$\sim$(const System.\-Numerics.\-Multiprecision.\-BigInt\&\-)}
& Returns bitwise complement of \textbf{BigInt}
 value.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.Abs.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{Abs(const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns absolute value of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.Numerics.Multiprecision.BigInt Abs(const System.Numerics.Multiprecision.BigInt\& x);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{2.65538cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
x
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& A \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}
\hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt}
\begin{flushleft}
Returns absolute value of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.ClearBit.R.System.Numerics.Multiprecision.BigInt.uint}{\subsubsection*{ClearBit(System.Numerics.Multiprecision.BigInt\&, uint) Function}}
\begin{flushleft}
Clear given bit of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public void ClearBit(System.Numerics.Multiprecision.BigInt\& x, uint bitIndex);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.94573cm}!{\raggedright}p{7.92093cm}!{\raggedright}p{4.93333cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
x
& \hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& A reference to a \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\\
bitIndex
& uint
& Index of bit to clear.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.SetBit.R.System.Numerics.Multiprecision.BigInt.uint}{\subsubsection*{SetBit(System.Numerics.Multiprecision.BigInt\&, uint) Function}}
\begin{flushleft}
Set given bit of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public void SetBit(System.Numerics.Multiprecision.BigInt\& x, uint bitIndex);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.94573cm}!{\raggedright}p{7.92093cm}!{\raggedright}p{4.93333cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
x
& \hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& A reference to a \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\\
bitIndex
& uint
& Index of bit to set.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.TestBit.R.System.Numerics.Multiprecision.BigInt.uint}{\subsubsection*{TestBit(System.Numerics.Multiprecision.BigInt\&, uint) Function}}
\begin{flushleft}
Returns true if given bit of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} is set, false otherwise.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public bool TestBit(System.Numerics.Multiprecision.BigInt\& x, uint bitIndex);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.94573cm}!{\raggedright}p{7.92093cm}!{\raggedright}p{4.93333cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
x
& \hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& A reference to a \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\\
bitIndex
& uint
& Index of bit to test.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}bool
\begin{flushleft}
Returns true if given bit of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} is set, false otherwise.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.ToggleBit.R.System.Numerics.Multiprecision.BigInt.uint}{\subsubsection*{ToggleBit(System.Numerics.Multiprecision.BigInt\&, uint) Function}}
\begin{flushleft}
Toggle given bit of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public void ToggleBit(System.Numerics.Multiprecision.BigInt\& x, uint bitIndex);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.94573cm}!{\raggedright}p{7.92093cm}!{\raggedright}p{4.93333cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
x
& \hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& A reference to a \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\\
bitIndex
& uint
& Index of bit to toggle.

\\
\end{supertabular}

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.remainder.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator\%(const System.Numerics.Multiprecision.BigInt\&, const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns the remainder when given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} is divided by another.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.Numerics.Multiprecision.BigInt operator\%(const System.Numerics.Multiprecision.BigInt\& left, const System.Numerics.Multiprecision.BigInt\& right);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{2.65538cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
left
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Divisor.

\\
right
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Dividend.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}
\hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt}
\begin{flushleft}
Returns the remainder when \hyperlink{System.Numerics.Multiprecision.operator.remainder.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt.left}{left} is divided by 
\hyperlink{System.Numerics.Multiprecision.operator.remainder.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt.right}{right}.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.and.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator\&(const System.Numerics.Multiprecision.BigInt\&, const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns bitwise AND of two \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} values.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.Numerics.Multiprecision.BigInt operator\&(const System.Numerics.Multiprecision.BigInt\& left, const System.Numerics.Multiprecision.BigInt\& right);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{3.66839cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
left
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Left operand.

\\
right
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Right operand.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}
\hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt}
\begin{flushleft}
Returns bitwise AND of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} values.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.times.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator*(const System.Numerics.Multiprecision.BigInt\&, const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns the product of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} value multiplied by another.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.Numerics.Multiprecision.BigInt operator*(const System.Numerics.Multiprecision.BigInt\& left, const System.Numerics.Multiprecision.BigInt\& right);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{3.66839cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
left
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Left operand.

\\
right
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Right operand.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}
\hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt}
\begin{flushleft}
Returns the product of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} value multiplied by another.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.plus.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator+(const System.Numerics.Multiprecision.BigInt\&, const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns the sum of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} value added to another.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.Numerics.Multiprecision.BigInt operator+(const System.Numerics.Multiprecision.BigInt\& left, const System.Numerics.Multiprecision.BigInt\& right);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{3.66839cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
left
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Left operand.

\\
right
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Right operand.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}
\hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt}
\begin{flushleft}
Returns the sum of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} value added to another.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.minus.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator-(const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns the negation of \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.Numerics.Multiprecision.BigInt operator-(const System.Numerics.Multiprecision.BigInt\& x);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{2.65538cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
x
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& A value.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}
\hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt}
\begin{flushleft}
Returns the negation of \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.minus.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator-(const System.Numerics.Multiprecision.BigInt\&, const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns the difference of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} value subtracted from another.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.Numerics.Multiprecision.BigInt operator-(const System.Numerics.Multiprecision.BigInt\& left, const System.Numerics.Multiprecision.BigInt\& right);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{3.66839cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
left
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Left operand.

\\
right
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Right operand.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}
\hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt}
\begin{flushleft}
Returns the difference of given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} value subtracted from another.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.divides.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator/(const System.Numerics.Multiprecision.BigInt\&, const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns the quotient when given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} is divided by another.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.Numerics.Multiprecision.BigInt operator/(const System.Numerics.Multiprecision.BigInt\& left, const System.Numerics.Multiprecision.BigInt\& right);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{2.65538cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
left
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Divisor.

\\
right
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Dividend.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}
\hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt}
\begin{flushleft}
Returns the quotient when given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} is divided by another.

\end{flushleft}
\subsubsection*{Remarks}
\begin{flushleft}
Quotient is rounded towards zero.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.less.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator$<$(const System.Numerics.Multiprecision.BigInt\&, const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns true if the first \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} is less than the second \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}, false otherwise.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public bool operator$<$(const System.Numerics.Multiprecision.BigInt\& left, const System.Numerics.Multiprecision.BigInt\& right);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{3.66839cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
left
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Left operand.

\\
right
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Right operand.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}bool
\begin{flushleft}
Returns true if the first \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} is less than the second \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}, false otherwise.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.shiftLeft.R.System.IO.OutputStream.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator$<$$<$(System.IO.OutputStream\&, const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Puts the value of the given \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} to the given output stream as string of decimal digits prefixed by minus sign if the value is negative.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.IO.OutputStream\& operator$<$$<$(System.IO.OutputStream\& s, const System.Numerics.Multiprecision.BigInt\& x);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{4.49442cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
s
& System.\-IO.\-OutputStream\&\-
& An output stream.

\\
x
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& A \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} value.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}System.\-IO.\-OutputStream\&\-
\begin{flushleft}
Returns a reference to the output stream.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.equal.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator==(const System.Numerics.Multiprecision.BigInt\&, const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns true if the first \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} is equal to the second \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}, false otherwise.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public bool operator==(const System.Numerics.Multiprecision.BigInt\& left, const System.Numerics.Multiprecision.BigInt\& right);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{3.66839cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
left
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Left operand.

\\
right
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Right operand.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}bool
\begin{flushleft}
Returns true if the first \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} is equal to the second \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt}, false otherwise.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.xor.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator\^{}(const System.Numerics.Multiprecision.BigInt\&, const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns bitwise XOR of two \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} values.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.Numerics.Multiprecision.BigInt operator\^{}(const System.Numerics.Multiprecision.BigInt\& left, const System.Numerics.Multiprecision.BigInt\& right);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{3.66839cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
left
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Left operand.

\\
right
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Right operand.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}
\hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt}
\begin{flushleft}
Returns bitwise XOR of two \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} values.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.or.C.R.System.Numerics.Multiprecision.BigInt.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator$|$(const System.Numerics.Multiprecision.BigInt\&, const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns bitwise inclusive OR of two \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} values.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.Numerics.Multiprecision.BigInt operator$|$(const System.Numerics.Multiprecision.BigInt\& left, const System.Numerics.Multiprecision.BigInt\& right);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{3.66839cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
left
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Left operand.

\\
right
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Right operand.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}
\hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt}
\begin{flushleft}
Returns bitwise inclusive OR of two \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} values.

\end{flushleft}
\clearpage

\hypertarget{System.Numerics.Multiprecision.operator.complement.C.R.System.Numerics.Multiprecision.BigInt}{\subsubsection*{operator$\sim$(const System.Numerics.Multiprecision.BigInt\&) Function}}
\begin{flushleft}
Returns bitwise complement of \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} value.

\end{flushleft}
\subsubsection*{Syntax}
\texttt{public System.Numerics.Multiprecision.BigInt operator$\sim$(const System.Numerics.Multiprecision.BigInt\& x);}
\subsubsection*{Parameters}
\begin{flushleft}
\begin{supertabular}[l]{!{\raggedright}p{1.30721cm}!{\raggedright}p{8.55945cm}!{\raggedright}p{2.65538cm}}
\textbf{Name}
& \textbf{Type}
& \textbf{Description}
\\
\hline
x
& \hyperlink{System.Numerics.Multiprecision.BigInt}{const System.\-Numerics.\-Multiprecision.\-BigInt\&\-}
& Operand.

\\
\end{supertabular}

\end{flushleft}
\subsubsection*{Returns}
\hyperlink{System.Numerics.Multiprecision.BigInt}{System.\-Numerics.\-Multiprecision.\-BigInt}
\begin{flushleft}
Returns bitwise complement of \hyperlink{System.Numerics.Multiprecision.BigInt}{BigInt} value.

\end{flushleft}
\clearpage
\end{document}


